Local simple connectedness of boundaries of hyperbolic groups

### 2020-03-10 paper.tex
Stopped worrying about something
Rearranged some todos

\todo{Worry about when $p^n_m$ is not defined.}

@@

\begin{lemma}\label{lem:describing_q_i}
  \todo{Check this version is strong enough.}
  Let $\zeta \in \boundary G$ be a point such that
  \begin{equation*}
    N_{2\delta+1}^{g_i\cdot S_{n_i}} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
        $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}} \subset H_i,
  \end{equation*}
  where $N_{2\delta+1}^{g_i\cdot S_{n_i}}$ denotes a $2\delta+1$-neighbourhood
  in $g_i\cdot S_{n_i}$ taken with respect to the metrid $\dist$.
  Then $\zeta \in U_i$ and $q_i(\zeta)$ is contained in the simplex of $H_i$
  spanned by this set of vertices.
\end{lemma}

@@

  In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
  $\delta$ of $x'$, for $i\geq i_0$. Furthermore, $\dist(g_i,x') = n_i$, so 
  $\dist(\eta_i(n_i), x')\leq 2\delta$. It follows from the description of
  $q_i$ in \cref{lem:describing_q_i} that $q_i(\zeta)$ is contained in a
  simplex with all vertices within a distance $4\delta+1$ of $x'$. The set of
  all such vertices spans a simplex, so, in particular, $q_i\restricted{C}$ and
  $q_{i_0}\restricted{C}$ are related by an affine homotopy for $i \geq i_0$. 
\end{proof}

@@

  Now, $\dist(x, H) \geq 9\delta+2$, so $\dist(z_j, H) \geq 5\delta+1$.
  Furthermore, $\gamma_j(n_i) \in H$. It follows that $\dist(\gamma_j(n_i), [z_1,
  z_2]) > \delta$ and so by considering a triangle with vertices $g_i$, $z_1$
  and $z_2$, $\dist(\gamma_1(n_i), \gamma_2(n_i)) \leq 2\delta$. The result
  follows by lemma~\ref{lem:describing_q_i}. 
\end{proof}

@@

\begin{proof}
  \todo{proof read the first htree paragraphs}
  Let $G$ satisfy $\ddag'_{C+D}$ with constants $L$ and $m_0 \geq n_0$.
  By increasing $m_0$ we can also assume that $G$ satisfies $\S_?$ with
  constants $L'$ and $m_0$.

>>>>

@@

\begin{lemma}\label{lem:describing_q_i}
  Let $\zeta \in \boundary G$ be a point such that
  \begin{equation*}
    N_{2\delta+1}^{g_i\cdot S_{n_i}} \set{\eta(n_i)\suchthat\text{$\eta$ a geodesic ray with
        $\eta(0) = g_i$ and $\eta(\infty) = \zeta$}} \subset H_i,
  \end{equation*}
  where $N_{2\delta+1}^{g_i\cdot S_{n_i}}$ denotes a $2\delta+1$-neighbourhood
  in $g_i\cdot S_{n_i}$ taken with respect to the metric $\dist$.
  Then $\zeta \in U_i$ and $q_i(\zeta)$ is contained in the simplex of $H_i$
  spanned by this set of vertices.
\end{lemma}

@@

  \todo{Is the lemma strong enough?}
  In summary, any geodesic ray from $g_i$ to $\zeta$ passes within a distance 
  $\delta$ of $x'$, for $i\geq i_0$. Furthermore, $\dist(g_i,x') = n_i$, so 
  $\dist(\eta_i(n_i), x')\leq 2\delta$. It follows from the description of
  $q_i$ in \cref{lem:describing_q_i} that $q_i(\zeta)$ is contained in a
  simplex with all vertices within a distance $4\delta+1$ of $x'$. The set of
  all such vertices spans a simplex, so, in particular, $q_i\restricted{C}$ and
  $q_{i_0}\restricted{C}$ are related by an affine homotopy for $i \geq i_0$. 
\end{proof}

@@

  Now, $\dist(x, H) \geq 9\delta+2$, so $\dist(z_j, H) \geq 5\delta+1$.
  Furthermore, $\gamma_j(n_i) \in H$. It follows that $\dist(\gamma_j(n_i), [z_1,
  z_2]) > \delta$ and so by considering a triangle with vertices $g_i$, $z_1$
  and $z_2$, $\dist(\gamma_1(n_i), \gamma_2(n_i)) \leq 2\delta$. The result
  follows by lemma~\ref{lem:describing_q_i}. 
  \todo{Is the lemma strong enough?}
\end{proof}

@@

\begin{proof}
  \todo{proof read the first three paragraphs}
  Let $G$ satisfy $\ddag'_{C+D}$ with constants $L$ and $m_0 \geq n_0$.
  By increasing $m_0$ we can also assume that $G$ satisfies $\S_?$ with
  constants $L'$ and $m_0$.
